\myTitle

### 2023-12-21 map-of-samples.Rmd
Finish the map and insert it into the TeX

our_rivers <- all_rivers %>%
  filter(gnis_name %in% c(
    "Sacramento River",
    "San Joaquin River",
    "Feather River",
    "Russian River",
    "Trinity River"
    #"Deer Creek",
    #"Battle Creek"
  ) | 
    gnis_id %in% c(
      "00220293", "00237425", "00263498", "00266522",  # these are butte creek
      "00233775", "01655075",    # these are deer
      "00218740", "00229640", "00234966"   # these are battle creek
    ) 
  ) %>%
  bind_rows(mill_candi)

@@

## Crop
```{r}
# important to put them in this order and named like this
domain <- c(
  xmin = -128,
  xmax = -116,
  ymin = 36,
  ymax = 42.5
)
nat_crop <- crop(nat.earth, y = ext(domain))
state_subset <- st_crop(state_prov, domain)
coastline_cropped <- st_crop(coastline, domain)

@@

# Make the base map
```{r base-map-with-sampling-sites}
base_map <- ggplot() +
  ggspatial::layer_spatial(nat_crop) +
  geom_sf(data = state_subset, color = "gray30", fill = NA) +
  geom_sf(data = coastline_cropped, color = "gray30", fill = NA) +
  geom_sf(data = our_rivers, colour = "blue")

base_map
```

@@

```{r}
base_map + 
  geom_point(data = labels, aes(x = label_long, y = label_lat), colour = "red") +
  geom_point(data = labels, aes(x = tip_long, y = tip_lat), colour = "blue", size = 0.2)
```

# Grab data for sampling sites

```{r}
fish_sites <- read_csv("./data/100-RoSA_sample_sites.csv")
```

```{r}

  geom_text(data = fish_sites, aes(x = name_long, y = name_lat, label = pop, family = "serif", fontface = font_type), size = 3.5) +
  geom_segment(data = fish_sites %>% filter(!pop %in% c("San Joaquin", "River (F)")), mapping = aes(x = line_long, xend = longitude, y = name_lat - 0.05, yend = latitude), size = 0.5) +
  geom_segment(data = fish_sites %>% filter(pop == "San Joaquin"), mapping = aes(x = line_long, xend = longitude, y = name_lat - 0.55, yend = latitude), size = 0.5) +
  geom_point(data = fish_sites, mapping = aes(x = longitude, y = latitude), fill = fish_sites$color2, colour = fish_sites$color2) +
  scale_x_continuous(expand = c(0, 0)) +
  xlab("Longitude") +
  scale_y_continuous("Latitude", expand = c(0, 0)) +
  coord_sf(xlim = domain[1:2], ylim = domain[3:4]) +
  scalebar(
    x.min = domain[1], x.max = domain[2], y.min = domain[3], y.max = domain[4],
    location = "bottomright", model = "WGS84", dist = 250, anchor = c(x = -123, y = 36), st.size = 2.5, transform = TRUE, dist_unit = "km"
  ) +
  theme_bw() +
  theme(
    panel.border = element_rect(colour = "black", size = 1),
    axis.text.x = element_text(size = 8, family = "serif", angle = 35, hjust = 1),
    axis.text.y = element_text(size = 8, family = "serif"),
    axis.title.y = element_text(family = "serif", size = 10),
    axis.title.x = element_text(family = "serif", vjust = 2, size = 10),
    plot.margin = margin(0, 0.1, 0, 0.15, "cm"),
    legend.position = "none"
  )

# base_map
```

## add north arrow to map.
```{r adding-arrow-to-base-map}
arrow_map <- base_map +
  north(x.min = domain[-1], x.max = domain[2], y.min = domain[3], y.max = domain[4], location = "bottomright", anchor = c(x = -120.25, y = 36.5))

# arrow_map
```

## Now, work on the world-scale map with the inset:
```{r inset-map}
wrld <- map_data("state")
domain_df <- data_frame(point = 1:length(domain), long = rep(domain[1:2], each = 2), lat = c(domain[3:4], rev(domain[3:4])))
inset_world <- ggplot() +
  geom_path(data = wrld, aes(x = long, y = lat, group = group), colour = "black", size = 0.1) +
  geom_polygon(data = domain_df, mapping = aes(x = long, y = lat), colour = "red", fill = "red", alpha = 0.3) +
  coord_map("ortho", orientation = c(41, -132, 0)) +
  theme_bw() +
  labs(x = NULL, y = NULL) +
  theme(
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    plot.margin = unit(c(0, 0, -1, -1), "mm")
  )
# inset_world
```

@@

```{r cowplot-to-make-inset}
final_map <- ggdraw() +
  draw_plot(arrow_map) +
  draw_plot(inset_world, x = 0.7, y = 0.725, width = 0.25, height = 0.2)

ggsave(final_map, filename = "./outputs/100/RoSA_figure1_map_with_inset.pdf", width = 4.75, height = 4.25)
# and then plot it in the notebook (albeit at different size) too
final_map
```

>>>>

our_rivers <- all_rivers %>%
  filter(gnis_name %in% c(
    "Sacramento River",
    "San Joaquin River",
    "Feather River",
    "Russian River",
    "Trinity River",
    "Klamath River"
    #"Deer Creek",
    #"Battle Creek"
  ) | 
    gnis_id %in% c(
      "00220293", "00237425", "00263498", "00266522",  # these are butte creek
      "00233775", "01655075",    # these are deer
      "00218740", "00229640", "00234966"   # these are battle creek
    ) 
  ) %>%
  bind_rows(mill_candi)

@@

## Crop
```{r}
# important to put them in this order and named like this
domain <- c(
  xmin = -127.9,
  xmax = -117.4,
  ymin = 36,
  ymax = 42.6
)
sf_use_s2(FALSE)
nat_crop <- crop(nat.earth, y = ext(domain))
state_subset <- st_crop(state_prov, domain)
coastline_cropped <- st_crop(coastline, domain)

@@

# Make the base map
```{r base-map-with-sampling-sites}
base_map <- ggplot() +
  ggspatial::layer_spatial(nat_crop) +
  geom_sf(data = state_subset, color = "gray30", fill = NA) +
  geom_sf(data = coastline_cropped, color = "gray30", fill = NA, linewidth = 0.15) +
  geom_sf(data = our_rivers, colour = "blue", linejoin = "round", lineend = "round")

@@

```{r}
bit <- 0.0
kick <- 0.4
source("R/colors.R")

labels_1line <- labels %>%
  group_by(name_text) %>%
  filter(rank == max(rank)) %>%
  ungroup()

mm <- base_map + 
  geom_segment(data = labels, aes(x = tip_long, y = tip_lat, xend = label_long, yend = label_lat), colour = "black", size = 0.4) +
  geom_point(data = labels, aes(x = label_long + bit + (1 - hjust * 2) * kick * (rank - 1), y = label_lat, fill = run_timing), shape = 21, size = 3.5) +
  geom_label(
    data = labels_1line,
    aes(
      x = label_long + bit + (1 - hjust * 2) * kick * ( 0.65 + rank - 1),
      y = label_lat, 
      label = name_text,
      hjust = hjust
    ),
    size = 2.2,
    label.padding = unit(0.09, "lines")
  ) +
  scale_fill_manual(values = run_time_colors) +
  theme_bw() +
  theme(
    panel.border = element_rect(colour = "black", linewidth = 1),
    axis.text.x = element_text(size = 8, family = "serif", angle = 35, hjust = 1),
    axis.text.y = element_text(size = 8, family = "serif"),
    axis.title.y = element_text(family = "serif", size = 10),
    axis.title.x = element_text(family = "serif", vjust = 2, size = 10),
    plot.margin = margin(0, 0.1, 0, 0.15, "cm"),
    legend.position = "none"
  ) +
  xlab("Longitude") +
  ylab("Latitude") +
  coord_sf(
    expand = FALSE,
  ) +
  guides(fill = guide_legend(title = "Run Timing:", nrow = 2)) +
  ggspatial::annotation_north_arrow(location = "br", height = unit(10, "mm"), width = unit(5, "mm"), style = north_arrow_fancy_orienteering()) +
  ggspatial::annotation_scale(location = "br", height = unit(0.1, "cm"))

## Now, work on the world-scale map with the inset:
```{r inset-map}
wrld <- map_data("world")
states <- map_data("state")
domain_df <- tibble(point = 1:length(domain), long = rep(domain[1:2], each = 2), lat = c(domain[3:4], rev(domain[3:4])))

inset_world <- ggplot() +
  geom_polygon(data = wrld, aes(x = long, y = lat, group = group), colour = "black", fill = "gray90", size = 0.1) +
  geom_path(data = states, aes(x = long, y = lat, group = group), colour = "black", size = 0.1) +
  geom_polygon(data = domain_df, mapping = aes(x = long, y = lat), colour = "red", fill = "red", alpha = 0.3, linewidth = 0.1) +
  coord_map("ortho", orientation = c(30, -114, 0), xlim = c(-150, -75), ylim = c(28, 60)) +
  theme_bw() +
  labs(x = NULL, y = NULL) +
  theme(
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    plot.margin = unit(c(0, 0, -1, -1), "mm")
  )
inset_world
```

@@

```{r cowplot-to-make-inset}
final_map <- ggdraw() +
  draw_plot(mm) +
  draw_plot(inset_world, x = 0.181, y = 0.139, width = 0.20, height = 0.17)

ggsave(final_map, filename = output_list$map, width = 5, height = 3.5)

# let's crop that down for use, too
CALL <- paste("pdfcrop ", output_list$map, collapse = " ")
system(CALL)

# Make colored ball for inclusion into the caption

We can do this and just kick them directly into the tex/images folder.  
```{r}
rc_col_tib <- enframe(run_time_colors) %>%
  mutate(
    nospace = str_replace_all(name, " ", "-"),
    file = str_c("tex/images/", nospace, "-ball.pdf")
  )

for(r in 1:nrow(rc_col_tib)) {
  tmp <- rc_col_tib[r,]
  g <- ggplot(tmp, aes(x = 1, y = 1)) +
    geom_point(shape = 21, fill = tmp$value, size = 3.5) +
    theme_void()
  ggsave(g, filename = tmp$file)

  CALL <- str_c("pdfcrop ", tmp$file)
  system(CALL)
  file.remove(tmp$file)
}
```

### 2023-12-21 tex/body-text-of-paper.tex
Update body-text-of-paper.tex
Finish the map and insert it into the TeX

Here, we present a reference baseline for Chinook salmon, targeted to the complex population 
structure within the Central Valley of California. Chinook salmon of the two main river basins---the 
Sacramento and the San Joaquin---within the Central Valley exhibit the greatest run-timing diversity
within the species.  With four recognized ecotypes, delineated primarily on the basis of run timing
(Fall-, Late-Fall-, Winter-, and Spring-run), adult Chinook salmon can be found migrating or residing
in freshwater every month of the year in California.

@@

More Verbiage.

>>>>

Here, we present a reference baseline for Chinook salmon, targeted to the complex population 
structure within the Central Valley of California. Chinook salmon of the two main river basins---the 
Sacramento and the San Joaquin---within the Central Valley exhibit the greatest run-timing diversity
within the species.  With four recognized ecotypes, delineated primarily on the basis of run timing
(Fall-, Late-Fall-, Winter-, and Spring-run), adult Chinook salmon can be found migrating or residing
in freshwater every month of the year in California. NEED MORE HERE.

@@

We sampled fish for the reference baselines from 8 locations on the across the two
main tributaries (the Sacramento River and the San Joaquin River) within
California's Central Valley. The baseline also includes samples collected from
one location in the Klamath River, and three rivers of the California coast
Fig.~\ref{fig:map}
%%%%%%%%%%%%%
\begin{figure}
\newcommand{\mapcap}{\footnotesize  A map of sampling locations within
California represented in the reference baseline.  The colored circles aside
each location name represent the different run-timing groups of Chinook salmon
included the samples from the location.  Color codes are as follows: \Wball~=~Winter run,
\LFball{}~=~Late-fall run, \Fball~=~Fall run, \Sball~=~Spring run.}
\begin{center}
\includegraphics[width=\columnwidth]{images/map-crop.pdf}
\end{center}
\caption[\mapcap]{\mapcap}
\label{fig:map}
\end{figure}
%%%%%%%%%%%%%%%

### 2023-12-21 tex/newcomms.tex
Finish the map and insert it into the TeX

>>>>

\newcommand{\LFball}{\raisebox{-0.12 em}{\includegraphics[height=1.02em]{images/Late-fall-run-ball-crop.pdf}}}
\newcommand{\Fball}{\raisebox{-0.12 em}{\includegraphics[height=1.02em]{images/Fall-run-ball-crop.pdf}}}
\newcommand{\Wball}{\raisebox{-0.12 em}{\includegraphics[height=1.02em]{images/Winter-run-ball-crop.pdf}}}
\newcommand{\Sball}{\raisebox{-0.12 em}{\includegraphics[height=1.02em]{images/Spring-run-ball-crop.pdf}}}
